---
title: "Introduction to R - Project Report"
author: 
    - "Silvan Hess, silvan.hess@stud.unilu.ch, S19-862-614"
    - "Lecturer: Dr. Fabian Jundt"
date: today
date-format: "D. MMMM YYYY"
format: html
# fontsize: 12pt
# linestretch: 1.5
# geometry: left=2.5cm,right=2.5cm,top=3cm,bottom=3cm
execute:
  echo: false
  warning: false
knitr:
  opts_chunk:
    message: false
---

```{r}
#| label: setup
#| message: false

# Load Packages
library(tidyverse)
library(haven)

```

## Introduction

The purpose of this Report is to get an overview over the survey data.

We look at the Variables:

-   Country, Gender, Age

-   Political Orientation

-   Trust in Political Institutions

-   Belief in Human Caused Climate Change

## Analyze Demographics

First, we look at which countries the survey took place in and how many people were surveyed in each country.

```{r}
# call barplot
read_rds("repo/barplot_countries_surveyed.rds")
```

Next, we look at the age distribution in the countries.

```{r}
# call violinplot
read_rds("repo/violinplot_age_per_country.rds")
```

## Visualize political orientation, trust and climate beliefs across demographics

In this chapter we investigate the relationship of age and political orientation, trust and climate change beliefs for different countries.

### Political Orientation

```{r}
#call facet barplot of political orientation
read_rds("repo/barplot_lr_self.rds")
```
### Trust in Political Institutions

```{r}
#call facet barplot of trust
read_rds("repo/barplot_trust.rds")
```

### Belief in Human Made Climate Change

```{r}
#call facet barplot of CC Belief
read_rds("repo/barplot_climate_change.rds")
```

# Appendix

## R Code

The following code was used in this Report:

```{r ref.label=knitr::all_labels()}
#| echo: true
#| eval: false

```
